BETTING AND BELIEF: PREDICTION MARKETS AND ATTRIBUTION OF CLIMATE CHANGE

### 2016-03-28 prediction_market_wsc.Rnw
small edit
Bio Martin

What is not clear to us is why increasing the number of traders slows convergence, even if the number of edges per trader remains fixed. This will be a topic for future research where we will be increasing the number of traders into the thousands.

@@

\noindent {\bf MARTIN VAN DER LINDEN} is a Ph.D. Candidate at Vanderbilt University. \\
\textbf{TODO: Martin, please fill this in.}\\
His email address is \email{martin.van.der.linden@vanderbilt.edu}, and website: \href{https://martinvdlinden.wordpress.com/}{https://martinvdlinden.wordpress.com/}.\\

>>>>

What is not clear to us is why increasing the number of traders slows convergence, even if the number of edges per trader remains fixed. This is a topic for future research.

@@

\noindent {\bf MARTIN VAN DER LINDEN} is a Ph.D. Candidate at Vanderbilt University. He studies the design and performances of market and institutions using tools from economic theory and game theory.
His email address is \email{martin.van.der.linden@vanderbilt.edu}, and website: \href{https://martinvdlinden.wordpress.com/}{https://martinvdlinden.wordpress.com/}.\\
